Binary companions of red giant stars in \apogee\ \DR

### 2018-02-28 paper/1-catalog/twoface-catalog.tex
results subsections

\todo{Describe catalog contents: Also include M2_min and primary mass when
possible?}

@@

\todo{Also include M2_min and primary mass when possible?}

@@

@@

>>>>

\todo{Describe catalog contents: Also include M2min and primary mass when
possible?}

@@

\todo{Also include M2min and primary mass when possible?}

@@

\subsection{Red clump stars lack short-period companions}

@@

\subsection{Evidence for tidal circularization at $P\sim 10~\textrm{day}$}

\subsection{Companion masses and mass ratios}

\subsection{Impossible companions}
